---
title: "Generate List of Used References"
output: html_notebook
---

# Description 

This notebook contains code that generates a list of used references from within a manuscript. The manuscript has to be in `txt` format. 
References need to be in the Form (Author Year) or (Author A Year; Author B Year) or (Author A Year, Author B Year). 
The output will be a list of all references used. The outuput will be sorted alhabetically. Brackets that contain multiple references will be split up accordingly, i.e. the above example will generate two entries in the output. There will be no duplicates in the output.
The output will be given directly inside the notebook and also saved as a `txt` file.

# Setup

Change the values below according to your needs. The vanilla implementation assumes that **the manuscript with which we will work is located in the same folder as this script**.

```{r set filenames}
# can also be set to a word document if the conversion option below is used
input_file_name <- 'manuscript.txt'
output_file_name <- 'references.txt'
```

## Conversion

If you are running a UNIX System (i.e., MacOS or Linux) and have `pandoc` installed, you can use the below code to let it convert your manuscript from `docx` to `txt`. Other options are copy-pasting the text into a document or saving as a `txt` file from within *Word*. 

```{r optional conversion}
# only run if a wordx document was specified above
# careful: data might get lost otherwise!
args <- paste(input_file_name, '-o', 'manuscript.txt')
system2(command = 'pandoc', args = args)
input_file_name <- 'manuscript.txt'Å
```

# Reference parsing

```{r}
source('reference_list_generator_helper.R')
reference_list <- generate_reference_list(input_file_name)
fileConn <- file(output_file_name)    
writeLines(reference_list, fileConn)    
close(fileConn)
reference_list
```


